% ---------------- PAGE 8 ----------------
\setcounter{page}{8}

\begin{enumerate}[label=\textbf{\arabic*.}, start=17, leftmargin=*, itemsep=22pt]

\item {\hindifont द्वितीय चतुर्थांश में ऐसे वृत्तों के कुल का अवकल समीकरण ज्ञात कीजिए जो निर्देशांक अक्षों को स्पर्श करते हैं।}\\[6pt]
Form the differential equation of the family of circles in the second quadrant and touching the coordinate axes.

\item {\hindifont $x$ के लिए हल कीजिए : $\sin^{-1}x+\sin^{-1}(1-x)=\cos^{-1}x$}\\[10pt]
\begin{center}
{\hindifont अथवा}\\[4pt]
\end{center}


{\hindifont यदि $\cos^{-1}\!\left(\dfrac{x}{a}\right)+\cos^{-1}\!\left(\dfrac{y}{b}\right)=\alpha$ है, तो सिद्ध कीजिए कि
$\dfrac{x^2}{a^2}-\dfrac{2xy}{ab}\cos\alpha+\dfrac{y^2}{b^2}=\sin^2\alpha$ है।}\\[10pt]



Solve the equation for $x$ : $\sin^{-1}x+\sin^{-1}(1-x)=\cos^{-1}x$.

\begin{center}
\textbf{OR}
\end{center}

If $\cos^{-1}\!\left(\dfrac{x}{a}\right)+\cos^{-1}\!\left(\dfrac{y}{b}\right)=\alpha$, prove that
$\dfrac{x^2}{a^2}-\dfrac{2xy}{ab}\cos\alpha+\dfrac{y^2}{b^2}=\sin^2\alpha$.

\item {\hindifont एक ट्रस्ट ने दो प्रकार के बाण्ड (अनुबन्ध पत्र) में धन निवेशित किया। पहले बाण्ड में 10\% ब्याज और दूसरे बाण्ड में 12\% ब्याज मिलता है। ट्रस्ट को ₹ 2,800 कुल ब्याज प्राप्त हुआ। परन्तु यदि ट्रस्ट ने अदला-बदली करके बाण्डों में धन लगाया होता, तो उसे ₹ 100 कम ब्याज प्राप्त होता। आव्यूह विधि से ज्ञात कीजिए कि ट्रस्ट ने कितना धन निवेशित किया। प्राप्त ब्याज को हेल्पएज इंडिया में दान किया जाएगा। इस प्रश्न में कौन-सा मूल्य दर्शाया गया है ?}\\[10pt]
A trust invested some money in two type of bonds. The first bond pays 10\% interest and second bond pays 12\% interest. The trust received ₹ 2,800 as interest. However, if trust had interchanged money in bonds, they would have got ₹ 100 less as interest. Using matrix method, find the amount invested by the trust. Interest received on this amount will be given to Helpage India as donation. Which value is reflected in this question ?

\end{enumerate}

\vfill
\noindent
65/1/C\hfill 
