% ---------------- PAGE 5 ----------------
\setcounter{page}{5}

\begin{enumerate}[leftmargin=*, label=\arabic*., start=8, itemsep=14mm]

\item
\textHindi{%
एक समांतर चतुर्भुज की दो आसन्न भुजाएँ
$2\hat{i}-4\hat{j}-5\hat{k}$ और $2\hat{i}+2\hat{j}+3\hat{k}$ हैं।
इसके दोनों विकर्णों के समांतर दो मात्रक सदिश ज्ञात कीजिए।
विकर्णों के सदिशों का प्रयोग करके समांतर चतुर्भुज का क्षेत्रफल ज्ञात कीजिए।
}\\[3mm]
The two adjacent sides of a parallelogram are
$2\hat{i}-4\hat{j}-5\hat{k}$ and $2\hat{i}+2\hat{j}+3\hat{k}$.
Find the two unit vectors parallel to its diagonals.
Using the diagonal vectors, find the area of the parallelogram.

\item
\textHindi{%
एक पासा फेंकने के खेल में एक व्यक्ति ₹~5 जीतता है यदि उसे 4 से बड़ी संख्या प्राप्त होती है,
अन्यथा वह ₹~1 हार जाता है।
वह व्यक्ति 3 बार पासा फेंकने का निर्णय लेता है लेकिन
चार से बड़ी संख्या प्राप्त करने पर खेल छोड़ देता है।
मनुष्य द्वारा जीती/हारी जाने वाली राशि की प्रत्याशा ज्ञात कीजिए।
}\\[3mm]
\begin{center}
\textHindi{\textbf{अथवा}}\\[2mm]
\end{center}
\vspace{6mm}
\textHindi{%
एक थैले में 4 गेंदें हैं।
यादृच्छया दो गेंदें बिना प्रतिस्थापना के निकाली गई
और दोनों सफेद पाई गईं।
इसकी क्या प्रायिकता है कि थैले में सभी गेंदें सफेद हैं?
}\\[3mm]


\end{enumerate}




In a game, a man wins ₹~5 for getting a number greater than 4
and loses ₹~1 otherwise, when a fair die is thrown.The man decided to throw a die thrice but to quit as and whenhe gets a number greater than 4.Find the expected value of the amount he wins/loses.\\[6mm]
\vspace{6mm}

\begin{center}
\textbf{OR}
\end{center}

\vspace{6mm}
A bag contains 4 balls.
Two balls are drawn at random (without replacement)
and are found to be white.
What is the probability that all balls in the bag are white?

\vfill

% Footer
\noindent
65/1/C\hfill \hfill \textbf{P.T.O.}
